Simulating and detecting recovery in closed areas

### 2021-11-16 analysis/sim.Rmd
Add note

```{r data-prep-model-fit, warning=FALSE, message=FALSE}
dat_to_fit <- readRDS(here("data-generated/dat_to_fit_hbll.rds"))
grid <- readRDS(here("data-generated/hbll-n-grid-w-restr.rds"))
grid$survey_abbrev <- "HBLL OUT N"
ll_removed <- readRDS(here("data-generated/hu_co_demersalfishing_bottomlongline_d_X.rds"))
d <- filter(dat_to_fit, species_common_name == "north pacific spiny dogfish")

m0 <- fit_geo_model(d, pred_grid = grid, survey = "HBLL",
  family = "tweedie",
  # MPA_trend = TRUE,
  return_model = TRUE, do_fit = FALSE)

>>>>

```{r data-prep-model-fit, warning=FALSE, message=FALSE}
dat_to_fit <- readRDS(here("data-generated/dat_to_fit_hbll.rds"))
grid <- readRDS(here("data-generated/hbll-n-grid-w-restr.rds"))
grid$survey_abbrev <- "HBLL OUT N"
# ll_removed <- readRDS(here("data-generated/hu_co_demersalfishing_bottomlongline_d_X.rds"))
d <- filter(dat_to_fit, species_common_name == "north pacific spiny dogfish")

# quick hack to get formatted data for fitting:
m0 <- fit_geo_model(d, pred_grid = grid, survey = "HBLL",
  family = "tweedie",
  # MPA_trend = TRUE,
  return_model = TRUE, do_fit = FALSE)
